\section{Grant of Rights}


\subsection{Purchase}
(i) Upon receipt of full payment, the Artist grants the Client a worldwide, 
non-exclusive, non-transferable, non-sublicensable, and revocable single user 
licence to use the Work for the purposes and within the limits specified in 
Section 3.
(ii) The work remains the property of the Artist until it has been paid in 
full by the Client.


\subsection{Rental}
Where the Work is rented, the licence granted in Section 2.1 is limited to the 
rental period stated in Schedule A. 
All rights revert automatically to the Artist upon expiry.


\subsection{Reservation of Rights}
(i) All rights not expressly granted / checked are reserved to the Artist.
(ii) The Artist reserves the right - unless otherwise agreed in writing - to 
sell, license, or otherwise commercially exploit the Work, whether on a 
stand-alone basis or bundled with other works or services, to any third party of 
the Artist's choosing, notwithstanding that the Work was expressly commissioned 
by or created for the Client.
(iii) The Artist reserves the right - unless otherwise agreed in a separate 
written instrument - to display, publish, reproduce, or otherwise make the Work 
(in whole or in part) publicly accessible, and to incorporate the Work into the 
Artist's portfolio, website, social-media channels, exhibitions, showreels, 
grant or competition submissions, or other self-promotional materials, 
notwithstanding that the Work was expressly commissioned by or created for the 
Client.


\subsection{Fees / Refunds}
All fees are non-refundable unless mandatory consumer law requires otherwise.
The Client acknowledges that they forfeit their right to any refunds upon the 
completion of the purchase and distribution of the Work to the Client.


\subsection{Future Support}
The Artist shall have no duty to furnish any updates, upgrades, maintenance, or 
other support services with respect to the Work, whether now or in the future, 
unless the Parties expressly agree otherwise in a separate written instrument.
